---
title: "STAT 331 Portfolio"
author: "Tyler Kinney"
format: html 
embed-resources: true
layout: margin-left
editor: visual
execute: 
  eval: false
  echo: true
---

[**My Grade:**]{.underline} I believe my grade equivalent to course work evidenced below to be an A-.

[**Learning Objective Evidence:**]{.underline} In the code chunks below, provide code from Lab or Challenge assignments where you believe you have demonstrated proficiency with the specified learning target. Be sure to specify **where** the code came from (e.g., Lab 4 Question 2).

## Working with Data

**WD-1: I can import data from a *variety* of formats (e.g., csv, xlsx, txt, etc.).**

-   `csv` Example 1

```{r}
#| label: wd-1-csv-1
# From Lab 2 Question 1 
surveys <- read_csv(here::here("Week 2", "Lab2", "Lab2_Data", "surveys.csv"))

```

-   `csv` Example 2

```{r}
#| label: wd-1-csv-2
Teacher_Eval <- read_csv(here::here('Week 3', 'Lab 3', 'teacher_evals.csv'))
```

-   `xlsx`

```{r}
#| label: wd-1-xlsx
# PA 4 Question 1
military <- read_xlsx("gov_spending_per_capita.xlsx",
                      sheet = "Share of Govt. spending",
                      skip  = 7,
                      n_max = 190,
                      na = c('..', '. .', 'xxx')
)
```

**WD-2: I can select necessary columns from a dataset.**

-   Example selecting specified columns

```{r}
#| label: wd-2-ex-1
# Lab 3 Question 5, revised
# Revision made the select function more condensed making use of :
teacher_evals_clean <- Teacher_Eval |>
  filter(no_participants > 9) |>
  rename(sex = gender)|>
  mutate(teacher_id = as.character(teacher_id),
         course_id = as.character(course_id)) |>
  select(course_id:SET_score_avg,
         percent_failed_cur,
         academic_degree:sex)
```

-   Example removing specified columns

```{r}
#| label: wd-2-ex-2
# Lab 9 question 6
evals |>
    distinct(teacher_id,
           .keep_all = TRUE) |>
    mutate('Academic Degree' = fct_recode(academic_degree,
             'No Degree' = 'no_dgr',
             'Masters' = 'ma',
             'Doctorate' = 'dr',
             'Tenured Professor' = 'prof'),
         'Seniority' =  case_when(
              seniority <= 4 ~ 'Junior',
              seniority >= 5 & seniority <= 8 ~ 'Senior',
              seniority >= 9 ~ 'Very Senior'),
         'Sex' = fct_recode(sex,
              'Male' = 'male',
              'Female' = 'female')
         ) |>
    select(-c(matches('^[[:lower:]]', ignore.case = F), starts_with('SET'))) |>
    pivot_longer(everything(),
               names_to = 'variable',
               values_to = 'level') |>
    count(variable, level) |>
    group_by(variable) |>
    mutate(prop = n/sum(n)) |>
    ungroup() |>
    gt(rowname_col = 'level',
       groupname_col = 'variable') |>
    cols_label(variable = md('**Demographic**'),
               level = md('**Group**'),
               n = md('**Count**'),
               prop = md('**%**')) |>
    tab_header(
    title = 'Demographics of Professors',
    subtitle = 'Student Evaluations at the University of Poland, Warsaw in 2020') |>
    tab_spanner(label = md('**Professors**'),
                columns = c(n, prop)) |>
    fmt_percent(columns = prop,
                decimals = 2) |>
    tab_options(row_group.background.color = 'grey',
                row_group.font.weight = 'bold')
```

-   Example selecting columns based on logical values (e.g., `starts_with()`, `ends_with()`, `contains()`, `where()`)

```{r}
#| label: wd-2-ex-3
# Lab 10 question 6
model_components <- tidy(linear_model_lm,
     conf.int = T,
     conf.level = 0.95) |>
  filter(term == 'x') |>
  select(estimate, starts_with('conf'))
```

**WD-3: I can filter rows from a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-3-numeric-ex-1
# Lab 4 Question 5
ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(Region, study_year) |>
  summarize(median_income = median(mhi_2018),
            .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_income,
              names_prefix = "Median income from ") |>
  arrange(desc(`Median income from 2018`))

```

-   Numeric Example 2

```{r}
#| label: wd-3-numeric-ex-2
# Lab 3 Question 10
teacher_evals_clean |>
  filter(question_no == 901) |>
  group_by(teacher_id) |>
  summarize(num_courses = n_distinct(course_id),
            avg_score_Q1 = mean(SET_score_avg)) |>
  filter(num_courses >= 5) |>
  arrange(avg_score_Q1) |>
  slice(-(2:46))
```

-   Character Example 1 (any context)

```{r}
#| label: wd-3-character
# Lab 5 Invesigating the Crime
crime_scene_report |>
  mutate(date = ymd(date)) |>
  filter(date == mdy('January 15, 2018'),
         type == 'murder',
         city == 'SQL City') |>
  pull(var = 3)
```

-   Character Example 2 (example must use functions from **stringr**)

```{r}
#| label: wd-3-string
# PA 5.1 Questions 1,2,3
message_data |>
filter(str_detect(Word, pattern = "^(m|M)"),
       str_detect(Word, pattern = "(z|Z)$"),
       str_detect(Word, pattern = "[:punct:]"))

```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-3-date
# PA 5.2 question 3 Revised
# Revised to include a negative filter, to better correspond with the given instructions
suspect <- suspect |>
  filter(!wday(Time.Spotted, label = TRUE, abbr = FALSE) %in% c("Tuesday", "Thursday"))
glimpse(suspect)
```

**WD-4: I can modify existing variables and create new variables in a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-4-numeric-ex-1
# 
```

-   Numeric Example 2

```{r}
#| label: wd-4-numeric-ex-2

```

-   Factor Example 1 (renaming levels)

```{r}
#| label: wd-4-factor-ex-1
# Lab 4 Question 7 Revised
# Feedback: Can you get your facet labels to be the same as mine? Can you reorder the facets so they go in the same order as mine?

#Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

#I like your colors! Can you find which ones I used?

# Revision: Reordered factors, added brewer.pal to match the colors
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare (USD)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018)) +
  scale_y_continuous(labels = scales::label_dollar())
```

-   Factor Example 2 (reordering levels)

```{r}
#| label: wd-4-factor-ex-2
# Lab 4 Question 7
# Lab 4 Question 7 Revised
# Feedback: Can you get your facet labels to be the same as mine? Can you reorder the facets so they go in the same order as mine?

#Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

#I like your colors! Can you find which ones I used?

# Revision: Reordered factors, added brewer.pal to match the colors
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare (USD)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018)) +
  scale_y_continuous(labels = scales::label_dollar())
```

-   Character (example must use functions from **stringr**)

```{r}
#| label: wd-4-string

```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-4-date
# Lab 5 After Checking Witness Interviews
follow_up_witness_2 <- get_fit_now_check_in |>
  mutate(check_in_date = ymd(check_in_date)) |>
  filter(month(check_in_date) == 01,
         day(check_in_date) == 09,
         year(check_in_date) == 2018,
         membership_id %in% follow_up_witness_1$id)|>
  left_join(follow_up_witness_1, by = join_by(membership_id == id)) |>
  left_join(person, by = c("name" = "name"))
```

**WD-5: I can use mutating joins to combine multiple dataframes.**

-   `left_join()` Example 1

```{r}
#| label: wd-5-left-ex-1
# Lab 5 After Checking Witness Interviews
follow_up_witness_2 <- get_fit_now_check_in |>
  mutate(check_in_date = ymd(check_in_date)) |>
  filter(month(check_in_date) == 01,
         day(check_in_date) == 09,
         year(check_in_date) == 2018,
         membership_id %in% follow_up_witness_1$id)|>
  left_join(follow_up_witness_1, by = join_by(membership_id == id)) |>
  left_join(person, by = c("name" = "name"))
```

-   `right_join()` Example 1

```{r}
#| label: wd-5-right

```

-   `left_join()` **or** `right_join()` Example 2

```{r}
#| label: wd-5-left-right-ex-2
# Lab 5 After Checking Shooters Interview
  facebook_event_checkin |>
  filter(person_id %in% potential_hirers$id) |>
  left_join(potential_hirers, by = c("person_id" = "id")) |>
  mutate(date = ymd(date)) |>
  select(name, event_name, date) |>
  filter(month(date) == 12,
         year(date) == 2017,
         event_name == 'SQL Symphony Concert') |>
    group_by(name) |>
    count(event_name)
```

-   `inner_join()` Example 1

```{r}
#| label: wd-5-inner-ex-1
# Lab 5 After Checking Witness Interviews Revised
# Revision: used inner join instead of left join to fit this goal
follow_up_witness_2 <- get_fit_now_check_in |>
  mutate(check_in_date = ymd(check_in_date)) |>
  filter(month(check_in_date) == 01,
         day(check_in_date) == 09,
         year(check_in_date) == 2018,
         membership_id %in% follow_up_witness_1$id)|>
  inner_join(follow_up_witness_1, by = join_by(membership_id == id)) |>
  left_join(person, by = c("name" = "name"))
```

-   `inner_join()` Example 2

```{r}
#| label: wd-5-inner-ex-2
# Lab 5 After Checking Witness Interviews Revised
# Revision: used inner join instead of left join to fit this goal
witness_testimonies_follow_up <- drivers_license |>
  filter(id == follow_up_witness_2$license_id,
         str_detect(plate_number, 'H42W')) |>
  inner_join(follow_up_witness_2, by = c('id' = 'license_id'))
```

**WD-6: I can use filtering joins to filter rows from a dataframe.**

-   `semi_join()`

```{r}
#| label: wd-6-semi

```

-   `anti_join()`

```{r}
#| label: wd-6-anti

```

**WD-7: I can pivot dataframes from long to wide and visa versa**

-   `pivot_longer()`

```{r}
#| label: wd-7-long
# Lab 4 Question 7 Revised
# Feedback: Can you get your facet labels to be the same as mine? Can you reorder the facets so they go in the same order as mine?

#Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

#I like your colors! Can you find which ones I used?

# Revision: Reordered factors, added brewer.pal to match the colors
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare (USD)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018)) +
  scale_y_continuous(labels = scales::label_dollar())
```

-   `pivot_wider()`

```{r}
#| label: wd-7-wide
# Lab 4 Question 5
ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(Region, study_year) |>
  summarize(median_income = median(mhi_2018),
            .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_income,
              names_prefix = "Median income from ") |>
  arrange(desc(`Median income from 2018`))
```

## Reproducibility

**R-1: I can create professional looking, reproducible analyses using RStudio projects, Quarto documents, and the here package.**

The following assignments satisfy the above criteria:

-   Example 1: Lab 2
-   Example 2: Lab 3
-   Example 3: Lab 4
-   Example 4: Lab 5
-   Example 5: Challenge 4

**R-2: I can write well documented and tidy code.**

-   Example of **ggplot2** plotting

```{r}
#| label: r-2-1
# Challenge 4 Graph
ca_childcare |>
group_by(Region, study_year) |>
  summarize(Overall_avg_Family_Cost = (mean(mfcc_infant) +
                               mean(mfcc_toddler) +
                               mean(mfcc_preschool)) / 3,
    Overall_avg_Center_Cost = (mean(mc_infant) +
                               mean(mc_toddler) +
                               mean(mc_preschool)) / 3,
    .groups = "drop") |>
  ggplot(mapping = aes(x = Overall_avg_Family_Cost,
                       y = Overall_avg_Center_Cost,
                       color = Region)) +
  geom_point() +
  facet_wrap(~ study_year) +
  labs(
  title = 'As Household Income Increases, Center-Based Infant Care Becomes More Expensive',
  subtitle = 'Average weekly costs (children aged 0–54 months) by region and study year',
  x = 'Average Weekly Family Childcare Cost',
  y = 'Average Weekly Center-Based Childcare Cost',
  color = "California Region") +
  theme_bw() +
  scale_color_brewer(palette = 'Set3') +
  scale_y_continuous(labels = scales::label_dollar()) +
  scale_x_continuous(labels = scales::label_dollar())
```

-   Example of **dplyr** pipeline

```{r}
#| label: r-2-2
# Lab 3 Question 7
teacher_evals_clean |>
  distinct(teacher_id, .keep_all = TRUE) |>
  select(teacher_id,
         sex,
         academic_degree,
         seniority) |>
  count(sex, academic_degree, seniority) |>
  group_by(academic_degree) |>
  summarize(academic_degree_count = sum(n))
```

-   Example of function formatting

```{r}
#| label: r-2-3

```

**R-3: I can write robust programs that are resistant to changes in inputs.**

-   Example (any context)

```{r}
#| label: r-3-example
# Lab 3 question 9
teacher_evals_clean |>
  group_by(teacher_id, course_id) |>
  summarize(number_questions = n_distinct(question_no)) |>
  filter(number_questions == 9) |>
  nrow()
```

-   Example (function stops)

```{r}
#| label: r-3-function-stops
# Lab 7 question 4
rescale_01 <- function(x){
  if(is.numeric(x) & length(x) > 1){
    (x - min(x, na.rm = TRUE)) / 
           (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
    }
  else{
    stop('Error: input is non-numeric')
  }
}
```

## Data Visualization & Summarization

**DVS-1: I can create visualizations for a *variety* of variable types (e.g., numeric, character, factor, date)**

-   At least two numeric variables

```{r}
#| label: dvs-1-num
# Challenge 4 Graph Revised
# Feedback: Progressing DVS-2, and Statisfactory DVS-3
# Revision: Found a non-standard color palette I like, added dollar sign labels, added some alpha to my points for easier viewing
ca_childcare |>
group_by(Region, study_year) |>
  summarize(Overall_avg_Family_Cost = (mean(mfcc_infant) +
                               mean(mfcc_toddler) +
                               mean(mfcc_preschool)) / 3,
    Overall_avg_Center_Cost = (mean(mc_infant) +
                               mean(mc_toddler) +
                               mean(mc_preschool)) / 3,
    .groups = "drop") |>
  ggplot(mapping = aes(x = Overall_avg_Family_Cost,
                       y = Overall_avg_Center_Cost,
                       color = Region)) +
  geom_point(alpha = 0.7) +
  facet_wrap(~ study_year) +
  labs(
  title = 'As Household Income Increases, Center-Based Infant Care Becomes More Expensive',
  subtitle = 'Average weekly costs (children aged 0–54 months) by region and study year',
  x = 'Average Weekly Family Childcare Cost',
  y = 'Average Weekly Center-Based Childcare Cost',
  color = "California Region") +
  theme_bw() +
  scale_color_brewer(palette = 'Set3') +
  scale_y_continuous(labels = scales::label_dollar()) +
  scale_x_continuous(labels = scales::label_dollar())
```

-   At least one numeric variable and one categorical variable

```{r}
#| label: dvs-2-num-cat
# Lab 2 Question 17 Revised
# Feedback: Do you need to rotate the y-axis labels? Is there a way you can make this boxplot without making people tilt their head to read the titles of your plot?
# Revision: Got rid of rotated y-axis text
blue_scheme<-c('#4682B4','#4A7E84')
ggplot(data = surveys,
       mapping = aes(x = weight, y = species, color = sex))+
  geom_boxplot(outliers = FALSE) + 
  scale_color_manual(values = blue_scheme) + 
  geom_jitter(color = '#FA807220', alpha = 0.2) +
  labs(x = 'Weight(g)',
       y = 'Species Type',
       title = 'How Does Weight Differ Among Species of Rodents?',
       subtitle = "Separated by <span style='color:#4682B4;'>Female</span> and <span style='color:#4A7E84;'>Male</span>") +
  theme(axis.text.y = element_text(size = 12),
        panel.background = element_rect(fill = 'lightgrey'),
        panel.border = element_rect(color = '#FA8072', size = 2),
        legend.position = 'none',
        plot.subtitle = element_markdown())
```

-   At least two categorical variables

```{r}
#| label: dvs-2-cat
# Lab 4 Question 7 Revised
# Feedback: Can you get your facet labels to be the same as mine? Can you reorder the facets so they go in the same order as mine?

#Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

#I like your colors! Can you find which ones I used?

# Revision: Reordered factors, added brewer.pal to match the colors
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare (USD)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018)) +
  scale_y_continuous(labels = scales::label_dollar())
```

-   Dates (time series plot)

```{r}
#| label: dvs-2-date
# Lab 4 Question 7 Revised
# Feedback: Can you get your facet labels to be the same as mine? Can you reorder the facets so they go in the same order as mine?

#Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

#I like your colors! Can you find which ones I used?

# Revision: Reordered factors, added brewer.pal to match the colors
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare (USD)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018)) +
  scale_y_continuous(labels = scales::label_dollar())
```

**DVS-2: I use plot modifications to make my visualization clear to the reader.**

-   I can modify my plot theme to be more readable

```{r}
#| label: dvs-2-ex-1
# Lab 4 Question 7 Revised
# Feedback: Can you get your facet labels to be the same as mine? Can you reorder the facets so they go in the same order as mine?

#Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

#I like your colors! Can you find which ones I used?

# Revision: Reordered factors, added brewer.pal to match the colors
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare (USD)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018)) +
  scale_y_continuous(labels = scales::label_dollar())
```

-   I can modify my colors to be accessible to anyone's eyes

```{r}
#| label: dvs-2-ex-2
# Challenge 4 Graph Revised
# Feedback: Progressing DVS-2, and Statisfactory DVS-3
# Revision: Found a non-standard color palette I like, added dollar sign labels, added some alpha to my points for easier viewing
ca_childcare |>
group_by(Region, study_year) |>
  summarize(Overall_avg_Family_Cost = (mean(mfcc_infant) +
                               mean(mfcc_toddler) +
                               mean(mfcc_preschool)) / 3,
    Overall_avg_Center_Cost = (mean(mc_infant) +
                               mean(mc_toddler) +
                               mean(mc_preschool)) / 3,
    .groups = "drop") |>
  ggplot(mapping = aes(x = Overall_avg_Family_Cost,
                       y = Overall_avg_Center_Cost,
                       color = Region)) +
  geom_point(alpha = 0.7) +
  facet_wrap(~ study_year) +
  labs(
  title = 'As Household Income Increases, Center-Based Infant Care Becomes More Expensive',
  subtitle = 'Average weekly costs (children aged 0–54 months) by region and study year',
  x = 'Average Weekly Family Childcare Cost',
  y = 'Average Weekly Center-Based Childcare Cost',
  color = "California Region") +
  theme_bw() +
  scale_color_brewer(palette = 'Set3') +
  scale_y_continuous(labels = scales::label_dollar()) +
  scale_x_continuous(labels = scales::label_dollar())
```

-   I can modify my plot titles to clearly communicate the data context

```{r}
#| label: dvs-2-ex-3
# Lab 2 Question 17 Revised
# Feedback: Do you need to rotate the y-axis labels? Is there a way you can make this boxplot without making people tilt their head to read the titles of your plot?
# Revision: Got rid of rotated y-axis text
blue_scheme<-c('#4682B4','#4A7E84')
ggplot(data = surveys,
       mapping = aes(x = weight, y = species, color = sex))+
  geom_boxplot(outliers = FALSE) + 
  scale_color_manual(values = blue_scheme) + 
  geom_jitter(color = '#FA807220', alpha = 0.2) +
  labs(x = 'Weight(g)',
       y = 'Species Type',
       title = 'How Does Weight Differ Among Species of Rodents?',
       subtitle = "Separated by <span style='color:#4682B4;'>Female</span> and <span style='color:#4A7E84;'>Male</span>") +
  theme(axis.text.y = element_text(size = 12),
        panel.background = element_rect(fill = 'lightgrey'),
        panel.border = element_rect(color = '#FA8072', size = 2),
        legend.position = 'none',
        plot.subtitle = element_markdown())
```

-   I can modify the text in my plot to be more readable

```{r}
#| label: dvs-2-ex-4
# Lab 4 Question 7 Revised
# Feedback: Can you get your facet labels to be the same as mine? Can you reorder the facets so they go in the same order as mine?

#Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

#I like your colors! Can you find which ones I used?

# Revision: Reordered factors, added brewer.pal to match the colors
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare (USD)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018)) +
  scale_y_continuous(labels = scales::label_dollar())
```

-   I can reorder my legend to align with the colors in my plot

```{r}
#| label: dvs-2-ex-5
# Lab 4 Question 7 Revised
# Feedback: Can you get your facet labels to be the same as mine? Can you reorder the facets so they go in the same order as mine?

#Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

#I like your colors! Can you find which ones I used?

# Revision: Reordered factors, added brewer.pal to match the colors
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare (USD)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018)) +
  scale_y_continuous(labels = scales::label_dollar())
```

**DVS-3: I show creativity in my visualizations**

-   I can use non-standard colors (Example 1)

```{r}
#| label: dvs-3-1-ex-1
# Lab 4 Question 7 Revised
# Feedback: Can you get your facet labels to be the same as mine? Can you reorder the facets so they go in the same order as mine?

#Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

#I like your colors! Can you find which ones I used?

# Revision: Reordered factors, added brewer.pal to match the colors
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare (USD)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018)) +
  scale_y_continuous(labels = scales::label_dollar())
```

-   I can use non-standard colors (Example 2)

```{r}
#| label: dvs-3-1-ex-2
# Lab 2 Question 17 Revised
# Feedback: Do you need to rotate the y-axis labels? Is there a way you can make this boxplot without making people tilt their head to read the titles of your plot?
# Revision: Got rid of rotated y-axis text
blue_scheme<-c('#4682B4','#4A7E84')
ggplot(data = surveys,
       mapping = aes(x = weight, y = species, color = sex))+
  geom_boxplot(outliers = FALSE) + 
  scale_color_manual(values = blue_scheme) + 
  geom_jitter(color = '#FA807220', alpha = 0.2) +
  labs(x = 'Weight(g)',
       y = 'Species Type',
       title = 'How Does Weight Differ Among Species of Rodents?',
       subtitle = "Separated by <span style='color:#4682B4;'>Female</span> and <span style='color:#4A7E84;'>Male</span>") +
  theme(axis.text.y = element_text(size = 12),
        panel.background = element_rect(fill = 'lightgrey'),
        panel.border = element_rect(color = '#FA8072', size = 2),
        legend.position = 'none',
        plot.subtitle = element_markdown())
```

-   I can use annotations (e.g., `geom_text()`)

```{r}
#| label: dvs-3-2

```

-   I can choose creative geometries (e.g., `geom_segment()`, `geom_ribbon)()`)

```{r}
#| label: dvs-3-3

```

**DVS-4: I can calculate numerical summaries of variables.**

-   Example using `summarize()`

```{r}
#| label: dvs-4-summarize
#Lab 3 Question 10
teacher_evals_clean |>
  filter(question_no == 901) |>
  group_by(teacher_id) |>
  summarize(num_courses = n_distinct(course_id),
            avg_score_Q1 = mean(SET_score_avg)) |>
  filter(num_courses >= 5) |>
  arrange(avg_score_Q1) |>
  slice(-(2:46))
```

-   Example using `across()`

```{r}
#| label: dvs-4-across

```

**DVS-5: I can find summaries of variables across multiple groups.**

-   Example 1

```{r}
#| label: dvs-5-1
# Lab 4 Question 5
ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(Region, study_year) |>
  summarize(median_income = median(mhi_2018),
            .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_income,
              names_prefix = "Median income from ") |>
  arrange(desc(`Median income from 2018`))
```

-   Example 2

```{r}
#| label: dvs-5-2
# Lab 3 Question 9
teacher_evals_clean |>
  group_by(teacher_id, course_id) |>
  summarize(number_questions = n_distinct(question_no)) |>
  filter(number_questions == 9) |>
  nrow()
```

**DVS-6: I can create tables which make my summaries clear to the reader.**

-   I can modify my column names to clearly communicate the data context

```{r}
#| label: dvs-6-ex-1
# Lab 4 Question 5
ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(Region, study_year) |>
  summarize(median_income = median(mhi_2018),
            .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_income,
              names_prefix = "Median income from ") |>
  arrange(desc(`Median income from 2018`))
```

-   I can modify the text in my table to be more readable (e.g., bold face for column headers)

```{r}
#| label: dvs-6-ex-2

```

-   I can arrange my table to have an intuitive ordering

```{r}
#| label: dvs-6-ex-3
# Lab 4 Question 5
ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(Region, study_year) |>
  summarize(median_income = median(mhi_2018),
            .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_income,
              names_prefix = "Median income from ") |>
  arrange(desc(`Median income from 2018`))
```

**DVS-7: I show creativity in my tables.**

-   I can use non-default colors

```{r}
#| label: dvs-7-ex-1
```

-   I can modify the layout of my table to be more readable (e.g., `pivot_longer()` or `pivot_wider()`)

```{r}
#| label: dvs-7-ex-2
# Lab 4 Question 5
ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(Region, study_year) |>
  summarize(median_income = median(mhi_2018),
            .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_income,
              names_prefix = "Median income from ") |>
  arrange(desc(`Median income from 2018`))
```

## Program Efficiency

**PE-1: I can write concise code which does not repeat itself.**

-   using a single function call with multiple inputs (rather than multiple function calls)

```{r}
#| label: pe-1-one-call
# Lab 5 Beginning
crime_scene_report |>
  mutate(date = ymd(date)) |>
  filter(date == mdy('January 15, 2018'),
         type == 'murder',
         city == 'SQL City') |>
  pull(var = 3)
```

-   using `across()`

```{r}
#| label: pe-1-across
# Lab 3 Question 5 Revised
# Revision to include across function to condense code
teacher_evals_clean <- Teacher_Eval |>
  filter(no_participants > 9) |>
  rename(sex = gender) |>
  mutate(across(c(teacher_id, course_id), .fns = as.character)) |>
  select(course_id:SET_score_avg,
         percent_failed_cur,
         academic_degree:sex)
```

-   using functions from the `map()` family

```{r}
#| label: pe-1-map-1

```

**PE-2: I can write functions to reduce repetition in my code.**

-   Example 1: Function that operates on vectors

```{r}
#| label: pe-2-1

```

-   Example 2: Function that operates on data frames

```{r}
#| label: pe-2-2

```

-   Example 3: Function that operates on vectors *or* data frames

```{r}
#| label: pe-2-3

```

**PE-3:I can use iteration to reduce repetition in my code.**

-   using `across()`

```{r}
#| label: pe-3-across
# Lab 3 Question 5 Revised
# Revision to include across function to condense code
teacher_evals_clean <- Teacher_Eval |>
  filter(no_participants > 9) |>
  rename(sex = gender) |>
  mutate(across(c(teacher_id, course_id), .fns = as.character)) |>
  select(course_id:SET_score_avg,
         percent_failed_cur,
         academic_degree:sex)
```

-   using a `map()` function with **one** input (e.g., `map()`, `map_chr()`, `map_dbl()`, etc.)

```{r}
#| label: pe-3-map-1

```

-   using a `map()` function with **more than one** input (e.g., `map_2()` or `pmap()`)

```{r}
#| label: pe-3-map-2

```

**PE-4: I can use modern tools when carrying out my analysis.**

-   I can use functions which are not superseded or deprecated

```{r}
#| label: pe-4-1
# Challenge 3 Question 1
Teacher_eval_chal <- Teacher_Eval |>
  filter(question_no == 903) |>
  mutate(SET_level =
        if_else(SET_score_avg >= 4,
                'excellent',
                'standard'),
        sen_level =
        case_when(
          seniority <= 4 ~ 'junior',
          seniority >= 5 & seniority <= 8 ~ 'senior',
          seniority >= 9 ~ 'very senior')) |>
  select(course_id, SET_level, sen_level)
```

-   I can connect a data wrangling pipeline into a `ggplot()`

```{r}
#| label: pe-4-2
# Lab 4 Question 7 Revised
# Feedback: Can you get your facet labels to be the same as mine? Can you reorder the facets so they go in the same order as mine?

#Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

#I like your colors! Can you find which ones I used?

# Revision: Reordered factors, added brewer.pal to match the colors
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare (USD)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018)) +
  scale_y_continuous(labels = scales::label_dollar())
```

## Data Simulation & Statisical Models

**DSSM-1: I can simulate data from a *variety* of probability models.**

-   Example 1

```{r}
#| label: dsm-1-1

```

-   Example 2

```{r}
#| label: dsm-1-2

```

**DSSM-2: I can conduct common statistical analyses in R.**

-   Example 1

```{r}
#| label: dsm-2-1
# Challenge 3 Question 
chisq.test(Teacher_eval_chal$SET_level, Teacher_eval_chal$sen_level)
```

-   Example 2

```{r}
#| label: dsm-2-2
# Lab 4 Question 9
reg_mod1 <- lm(mc_infant ~ mhi_2018, data = ca_childcare)
summary(reg_mod1)
```

-   Example 3

```{r}
#| label: dsm-2-3
# lab 2 Question 17
species_mod <- aov(weight ~ species, data = surveys) 
summary(species_mod)
```

## Revising My Thinking

I feel that a lot of my revisions throughout the course have less to do with answering the problem but rather how I approach solving the problem. Often times when I first submit labs and challenge I can get the desired result, but my process isn't great. I believe a lot of this has to do with how I am as a person, I'm always tempted to get stuff over with, my brain only focuses on the desired output and not about how I can make the output process cleaner or more robust. My revisions mainly correspond with feedback given on my original submissions of labs and challenges. Most of the revisions I did have to do with displaying data in a nicer fashion, and I believe now after receiving feedback on what to improve on with my graphing skills I feel confident about making better graphs on future assignments.

## Extending My Thinking

Honestly for me this aligns closely with what I said in the revising my thinking section, I feel that after getting feedback on my code the first few times, I have now realized it is important on how you output your answer and how you get their; The answer is not the only thing that matters. I also feel that my process of graph making has changed. At the beginning of the course I always thought about graph making from a very technical stand point, rather than a fun, creative way to display myself to who ever may be viewing my code. For instance in my challenge 4 graph I wanted to find a color scheme that I found fun and accessible to my viewers so I searched Google for color palettes and found Set3 which I really enjoy. Also before I started this course, I really didn't think about going back to my code to reflect on it. I feel that I didn't do this much before this class, because in CSC 101, the only other coding class I have taken, we weren't given much feedback and if I wasn't getting errors and got the right result, I would do well in the class, which is very different then the project based nature of this class, which aligns better with what I may do in the future.

## Peer Support & Collaboration

So far in the course I feel that my peer feedback has been lackluster, though I feel it is getting better every time I give some, so by the time the final portfolio is due, I should have some great feedback to put in here. So far, this is the best feedback I've given, which was to a peer on lab 4:

Overall I love the code formatting and how detailed you are in your explanation of the datset. Some things I noticed were that you probably didn't need to glimpse() in question 1, because it takes up a lot of space in the html, and doesn't provide a lot of information, also your labels didn't apply to your graph on question 8. I believe overall your answers to the questions are correct. Good Job.

I feel that in the collaborative activities I have done very well. I am willing to play whatever role is assigned to me, and if I am the one typing and the person thinking of the answer asks for my help, I try to point them in the direction I feel is best. When I have the other role, I am always doing what I feel is the best and after I complete a question, I ask my partner if they see a simpler solution, because I am still improving in making clean, short code. I also feel that when I am with my partner when we get really stuck or have a question about or code, we often raise our hand for help. For example in PA 5.2 question 3, we were trying to use a not in type operator, and we couldn't get it to work so we raised our hand for help, and you helped us try to format the idea correctly, but we couldn't get it to work at the time. But after reviewing the code after class, I figured out how to syntax it correctly. That exact code is under WD-3.
