---
title: "STAT 331 Portfolio"
author: "Tyler Kinney"
format: html 
embed-resources: true
layout: margin-left
editor: visual
execute: 
  eval: false
  echo: true
---

[**My Grade:**]{.underline} I believe my grade equivalent to course work evidenced below to be an \_\_.

[**Learning Objective Evidence:**]{.underline} In the code chunks below, provide code from Lab or Challenge assignments where you believe you have demonstrated proficiency with the specified learning target. Be sure to specify **where** the code came from (e.g., Lab 4 Question 2).

## Working with Data

**WD-1: I can import data from a *variety* of formats (e.g., csv, xlsx, txt, etc.).**

-   `csv` Example 1

```{r}
#| label: wd-1-csv-1
# From Lab 2 Question 1 
surveys <- read_csv(here::here("Week 2", "Lab2", "Lab2_Data", "surveys.csv"))

```

-   `csv` Example 2

```{r}
#| label: wd-1-csv-2
Teacher_Eval <- read_csv(here::here('Week 3', 'Lab 3', 'teacher_evals.csv'))
```

-   `xlsx`

```{r}
#| label: wd-1-xlsx
# PA 4 Question 1
military <- read_xlsx("gov_spending_per_capita.xlsx",
                      sheet = "Share of Govt. spending",
                      skip  = 7,
                      n_max = 190,
                      na = c('..', '. .', 'xxx')
)
```

**WD-2: I can select necessary columns from a dataset.**

-   Example selecting specified columns

```{r}
#| label: wd-2-ex-1
# Lab 3 Question 5, revised
teacher_evals_clean <- Teacher_Eval |>
  filter(no_participants > 9) |>
  rename(sex = gender)|>
  mutate(teacher_id = as.character(teacher_id),
         course_id = as.character(course_id)) |>
  select(course_id:SET_score_avg,
         percent_failed_cur,
         academic_degree:sex)
```

-   Example removing specified columns

```{r}
#| label: wd-2-ex-2
# PA 5.2 Question 3
suspect <- suspect |>
  filter(!wday(Time.Spotted, label = TRUE, abbr = FALSE) %in% c("Tuesday", "Thursday"))
glimpse(suspect)

```

-   Example selecting columns based on logical values (e.g., `starts_with()`, `ends_with()`, `contains()`, `where()`)

```{r}
#| label: wd-2-ex-3

```

**WD-3: I can filter rows from a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-3-numeric-ex-1
# Lab 4 Question 5
ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(Region, study_year) |>
  summarize(median_income = median(mhi_2018),
            .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_income,
              names_prefix = "Median income from ") |>
  arrange(desc(`Median income from 2018`))

```

-   Numeric Example 2

```{r}
#| label: wd-3-numeric-ex-1
# Lab 3 Question 10
teacher_evals_clean |>
  filter(question_no == 901) |>
  group_by(teacher_id) |>
  summarize(num_courses = n_distinct(course_id),
            avg_score_Q1 = mean(SET_score_avg)) |>
  filter(num_courses >= 5) |>
  arrange(avg_score_Q1) |>
  slice(-(2:46))
```

-   Character Example 1 (any context)

```{r}
#| label: wd-3-character
crime_scene_report |>
  mutate(date = ymd(date)) |>
  filter(date == mdy('January 15, 2018'),
         type == 'murder',
         city == 'SQL City') |>
  pull(var = 3)
```

-   Character Example 2 (example must use functions from **stringr**)

```{r}
#| label: wd-3-string
# PA 5.1 Questions 1,2,3
message_data |>
filter(str_detect(Word, pattern = "^(m|M)"),
       str_detect(Word, pattern = "(z|Z)$"),
       str_detect(Word, pattern = "[:punct:]"))

```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-3-date
# Lab 5 After Investigating the Shooter  
facebook_event_checkin |>
  filter(person_id %in% potential_hirers$id) |>
  left_join(potential_hirers, by = c("person_id" = "id")) |>
  mutate(date = ymd(date)) |>
  select(name, event_name, date) |>
  filter(month(date) == 12,
         year(date) == 2017,
         event_name == 'SQL Symphony Concert') |>
    group_by(name) |>
    count(event_name)
```

**WD-4: I can modify existing variables and create new variables in a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-4-numeric-ex-1
# 
```

-   Numeric Example 2

```{r}
#| label: wd-4-numeric-ex-2

```

-   Factor Example 1 (renaming levels)

```{r}
#| label: wd-4-factor-ex-1
# Lab 4 Question 7
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare ($)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018))
```

-   Factor Example 2 (reordering levels)

```{r}
#| label: wd-4-factor-ex-2
# Lab 4 Question 7
match_colors = colorRampPalette(RColorBrewer::brewer.pal(8, "Accent"))(10)

ca_childcare |>
  select(Region, study_year, mc_infant, mc_toddler, mc_preschool) |>
  pivot_longer(
    cols = mc_infant:mc_preschool,
    names_to = "Ages",
    values_to = "Weekly_Median") |>
  mutate(Ages = recode(Ages,
        mc_infant = "Infant",
        mc_toddler = "Toddler",
        mc_preschool = "Preschool"),
        Ages = factor(Ages, levels = c("Infant", "Toddler", "Preschool")),
        Region = fct_reorder2(Region, study_year, Weekly_Median))|>
  ggplot(mapping = aes(x = study_year,
                       y = Weekly_Median,
                       color = Region)) +
           geom_point() +
           geom_smooth() +
           facet_wrap(~Ages) +
  scale_color_manual(values = match_colors) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        plot.title = element_text(size = 10, face = 'bold')) +
  labs(x = 'Study Year',
       y = '',
       title = 'Weekly Median Price for Center-Based Childcare ($)',
       color = 'California Region') +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018),
                     labels = c(2008, 2010, 2012, 2014, 2016, 2018))
```

-   Character (example must use functions from **stringr**)

```{r}
#| label: wd-4-string

```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-4-date
# Lab 5 After Checking Witness Interviews
follow_up_witness_2 <- get_fit_now_check_in |>
  mutate(check_in_date = ymd(check_in_date)) |>
  filter(month(check_in_date) == 01,
         day(check_in_date) == 09,
         year(check_in_date) == 2018,
         membership_id %in% follow_up_witness_1$id)|>
  left_join(follow_up_witness_1, by = join_by(membership_id == id)) |>
  left_join(person, by = c("name" = "name"))
```

**WD-5: I can use mutating joins to combine multiple dataframes.**

-   `left_join()` Example 1

```{r}
#| label: wd-5-left-ex-1
# Lab 5 After Checking Witness Interviews
follow_up_witness_2 <- get_fit_now_check_in |>
  mutate(check_in_date = ymd(check_in_date)) |>
  filter(month(check_in_date) == 01,
         day(check_in_date) == 09,
         year(check_in_date) == 2018,
         membership_id %in% follow_up_witness_1$id)|>
  left_join(follow_up_witness_1, by = join_by(membership_id == id)) |>
  left_join(person, by = c("name" = "name"))
```

-   `right_join()` Example 1

```{r}
#| label: wd-5-right

```

-   `left_join()` **or** `right_join()` Example 2

```{r}
#| label: wd-5-left-right-ex-2
# Lab 5 After Checking Shooters Interview
  facebook_event_checkin |>
  filter(person_id %in% potential_hirers$id) |>
  left_join(potential_hirers, by = c("person_id" = "id")) |>
  mutate(date = ymd(date)) |>
  select(name, event_name, date) |>
  filter(month(date) == 12,
         year(date) == 2017,
         event_name == 'SQL Symphony Concert') |>
    group_by(name) |>
    count(event_name)
```

-   `inner_join()` Example 1

```{r}
#| label: wd-5-inner-ex-1

```

-   `inner_join()` Example 2

```{r}
#| label: wd-5-inner-ex-2

```

**WD-6: I can use filtering joins to filter rows from a dataframe.**

-   `semi_join()`

```{r}
#| label: wd-6-semi

```

-   `anti_join()`

```{r}
#| label: wd-6-anti

```

**WD-7: I can pivot dataframes from long to wide and visa versa**

-   `pivot_longer()`

```{r}
#| label: wd-7-long

```

-   `pivot_wider()`

```{r}
#| label: wd-7-wide

```

## Reproducibility

**R-1: I can create professional looking, reproducible analyses using RStudio projects, Quarto documents, and the here package.**

The following assignments satisfy the above criteria:

-   Example 1
-   Example 2
-   Example 3
-   Example 4
-   Example 5

**R-2: I can write well documented and tidy code.**

-   Example of **ggplot2** plotting

```{r}
#| label: r-2-1

```

-   Example of **dplyr** pipeline

```{r}
#| label: r-2-2

```

-   Example of function formatting

```{r}
#| label: r-2-3

```

**R-3: I can write robust programs that are resistant to changes in inputs.**

-   Example (any context)

```{r}
#| label: r-3-example

```

-   Example (function stops)

```{r}
#| label: r-3-function-stops

```

## Data Visualization & Summarization

**DVS-1: I can create visualizations for a *variety* of variable types (e.g., numeric, character, factor, date)**

-   At least two numeric variables

```{r}
#| label: dvs-1-num

```

-   At least one numeric variable and one categorical variable

```{r}
#| label: dvs-2-num-cat

```

-   At least two categorical variables

```{r}
#| label: dvs-2-cat

```

-   Dates (time series plot)

```{r}
#| label: dvs-2-date

```

**DVS-2: I use plot modifications to make my visualization clear to the reader.**

-   I can modify my plot theme to be more readable

```{r}
#| label: dvs-2-ex-1

```

-   I can modify my colors to be accessible to anyone's eyes

```{r}
#| label: dvs-2-ex-2

```

-   I can modify my plot titles to clearly communicate the data context

```{r}
#| label: dvs-2-ex-3

```

-   I can modify the text in my plot to be more readable

```{r}
#| label: dvs-2-ex-4

```

-   I can reorder my legend to align with the colors in my plot

```{r}
#| label: dvs-2-ex-5

```

**DVS-3: I show creativity in my visualizations**

-   I can use non-standard colors (Example 1)

```{r}
#| label: dvs-3-1-ex-1

```

-   I can use non-standard colors (Example 2)

```{r}
#| label: dvs-3-1-ex-2

```

-   I can use annotations (e.g., `geom_text()`)

```{r}
#| label: dvs-3-2

```

-   I can choose creative geometries (e.g., `geom_segment()`, `geom_ribbon)()`)

```{r}
#| label: dvs-3-3

```

**DVS-4: I can calculate numerical summaries of variables.**

-   Example using `summarize()`

```{r}
#| label: dvs-4-summarize

```

-   Example using `across()`

```{r}
#| label: dvs-4-across

```

**DVS-5: I can find summaries of variables across multiple groups.**

-   Example 1

```{r}
#| label: dvs-5-1

```

-   Example 2

```{r}
#| label: dvs-5-2

```

**DVS-6: I can create tables which make my summaries clear to the reader.**

-   I can modify my column names to clearly communicate the data context

```{r}
#| label: dvs-6-ex-1

```

-   I can modify the text in my table to be more readable (e.g., bold face for column headers)

```{r}
#| label: dvs-6-ex-2

```

-   I can arrange my table to have an intuitive ordering

```{r}
#| label: dvs-6-ex-3

```

**DVS-7: I show creativity in my tables.**

-   I can use non-default colors

```{r}
#| label: dvs-7-ex-1

```

-   I can modify the layout of my table to be more readable (e.g., `pivot_longer()` or `pivot_wider()`)

```{r}
#| label: dvs-7-ex-2

```

## Program Efficiency

**PE-1: I can write concise code which does not repeat itself.**

-   using a single function call with multiple inputs (rather than multiple function calls)

```{r}
#| label: pe-1-one-call

```

-   using `across()`

```{r}
#| label: pe-1-across

```

-   using functions from the `map()` family

```{r}
#| label: pe-1-map-1

```

**PE-2: I can write functions to reduce repetition in my code.**

-   Example 1: Function that operates on vectors

```{r}
#| label: pe-2-1

```

-   Example 2: Function that operates on data frames

```{r}
#| label: pe-2-2

```

-   Example 3: Function that operates on vectors *or* data frames

```{r}
#| label: pe-2-3

```

**PE-3:I can use iteration to reduce repetition in my code.**

-   using `across()`

```{r}
#| label: pe-3-across

```

-   using a `map()` function with **one** input (e.g., `map()`, `map_chr()`, `map_dbl()`, etc.)

```{r}
#| label: pe-3-map-1

```

-   using a `map()` function with **more than one** input (e.g., `map_2()` or `pmap()`)

```{r}
#| label: pe-3-map-2

```

**PE-4: I can use modern tools when carrying out my analysis.**

-   I can use functions which are not superseded or deprecated

```{r}
#| label: pe-4-1

```

-   I can connect a data wrangling pipeline into a `ggplot()`

```{r}
#| label: pe-4-2

```

## Data Simulation & Statisical Models

**DSSM-1: I can simulate data from a *variety* of probability models.**

-   Example 1

```{r}
#| label: dsm-1-1

```

-   Example 2

```{r}
#| label: dsm-1-2

```

**DSSM-2: I can conduct common statistical analyses in R.**

-   Example 1

```{r}
#| label: dsm-2-1

```

-   Example 2

```{r}
#| label: dsm-2-2

```

-   Example 3

```{r}
#| label: dsm-2-3

```

## Revising My Thinking

<!-- How did you revise your thinking throughout the course? How did you revise your thinking on the code examples you have provided in your portfolio? -->

<!-- For the revisions included in your Portfolio, to help me understand the nature of your revisions, please denote somehow the feedback I provided you (e.g., boldface, italics, colored text) before your revisions. -->

## Extending My Thinking

<!-- How did you extended your thinking throughout the course? How did you extend your thinking on the code examples you have provided in your portfolio? -->

## Peer Support & Collaboration

<!-- Include an image or a description of feedback you gave that you are proud of (either in a peer review or in Discord). -->

<!-- Include a description of how you grew as a collaborator through the weekly pair programming activities.   -->
